### 2022-12-01 README.Rmd
bump redirecting URLs

For questions and discussions about tidymodels packages, modeling, and machine learning, please [post on RStudio Community](https://rstd.io/tidymodels-community). If you think you have encountered a bug, please [submit an issue](https://github.com/tidymodels/infer/issues). Either way, learn how to create and share a [reprex](https://rstd.io/reprex) (a minimal, reproducible example), to clearly communicate about your code. Check out further details on [contributing guidelines for tidymodels packages](https://www.tidymodels.org/contribute/) and [how to get help](https://www.tidymodels.org/help/).

>>>>

For questions and discussions about tidymodels packages, modeling, and machine learning, please [post on RStudio Community](https://community.rstudio.com/new-topic?category_id=15&tags=tidymodels,question). If you think you have encountered a bug, please [submit an issue](https://github.com/tidymodels/infer/issues). Either way, learn how to create and share a [reprex](https://reprex.tidyverse.org/articles/learn-reprex.html) (a minimal, reproducible example), to clearly communicate about your code. Check out further details on [contributing guidelines for tidymodels packages](https://www.tidymodels.org/contribute/) and [how to get help](https://www.tidymodels.org/help/).
